Is there a Criterion in Criterial Learning? \\ \vspace{.08in} Insights from Studying Feedback Delays

### 2025-10-21 write/main_revision.tex
bug fix

Figure \ref{fig_exp_1_t2c}B shows the mean number of
problems solved in each condition of Experiment 1. A one-way
ANOVA revealed a significant effect of condition ($F(2, 39)
= 5.77$, $p < .01$, $\eta^2 = .23$). Planned comparisons
revealed that performance in the Delayed-Feedback condition
was significantly worse than in the Control condition
($t(18.54) = -3.28$, $p < .01$, $d=-1.21$) and worse than in
the Long ITI condition ($t(21.60) = -2.14$, $p < .05$,
$-.80$).  Performance in the Control and Long-ITI conditions
did not differ significantly from each other ($t(25.97) =
-1.50$, $p=.15$, $d=-.53$).

@@

Figure \ref{fig_exp_2_t2c}A shows the mean
trials-to-criterion in each condition of Experiment 2. An
independent-samples t-test revealed no significant effect of
condition ($t(32.0)=1.37$, $p = .18$, $d = .47$).  The mean
number of problems solved by each participant is shown in
Figure \ref{fig_exp_2_t2c}B. An independent-samples t-test
revealed no significant effect of condition ($t(32) =
-1.99$, $p = .06$, $d = -.68$).

>>>>

Figure \ref{fig_exp_1_t2c}B shows the mean number of
problems solved in each condition of Experiment 1. A one-way
ANOVA revealed a significant effect of condition ($F(2, 39)
= 5.77$, $p < .01$, $\eta^2 = .23$). Planned comparisons
revealed that performance in the Delayed-Feedback condition
was significantly worse than in the Control condition
($t(18.54) = -3.28$, $p < .01$, $d=-1.21$) and worse than in
the Long ITI condition ($t(21.60) = -2.14$, $p < .05$,
$d=-.80$).  Performance in the Control and Long-ITI
conditions did not differ significantly from each other
($t(25.97) = -1.50$, $p=.15$, $d=-.53$).

@@

Figure \ref{fig_exp_2_t2c}A shows the mean
trials-to-criterion in each condition of Experiment 2. An
independent-samples t-test revealed no significant effect of
condition ($t(32.0)=1.37$, $p = .18$, $d = .47$).  The mean
number of problems solved by each participant is shown in
Figure \ref{fig_exp_2_t2c}B. An independent-samples t-test
revealed no significant effect of condition ($t(32.0) =
-1.99$, $p = .06$, $d = -.68$).
